Causal Analysis Paper

### 2022-06-08 PaperAnalysis.Rmd
Heterogeinity of effects explanation added

### Positivity assumption

?
The second assumption is that of positivity, meaning that all units of analysis should have a nonzero probability of receiving either treatment.

### SUTVA

?
Finally, the third requirement is the stable unit treatment value assumption (SUTVA), meaning that there are no unmeasured versions of treatment and that the treatment status of any other unit does not affect other unit's outcomes.

@@

###Heterogeinity of effects

###G-separation

>>>>

@@

To estimate the effects of Abortion law flexibility on MMR, the authors of the paper fitted a fixed effects multiple regression model, in which they control for GDP, time, and countries, while trying to estimate the regression slope of flexible abortion law as a causal effect that is being studied:

[move Angelas equation here?]

This approach has been called "the workhorse model" used by researchers to estimate causal effects [@Aronov2016]. What fixed effects models do is that they remove all the unmeasured but group-specific confounding effects related to the unit that is being controlled. Controlling for unobserved counfounding related to countries and time is a common approach in studies such as these. However, this approach can have subtle consequences that limit the generalizibility of the findings.

@Aronov2016 showed that multiple regression estimates are actually weighted averages of unit-specific contributions. In cases when treatment effects are heterogeneous, in the sense that the effect of abortion law flexibility is not the same for every country, $\beta_L$ will not reflect ATE. Rather, it will be more strongly influenced by units that have more variability: many observations, large variations in abortion law flexibility and MMR, and that are hard to predict from country and time fixed effects and other controls (GDP, female primary education completion). This means that the estimated effect will be actually valid for a *sub-sample* of the population that is being studied. @Aronov2016 suggest that the *effective* sample, the sub-sample that has the strongest weights in the analysis should be reported explicitly so that it is more clear to which cases the effects generalise.
